### 2017-01-20 paper1.tex
paper1 and paper2 added correctly

\begin{figure}
\includegraphics[width=12.5 cm,angle=90]{month_density_occurance2010.pdf}
\caption{Monthly average plots of echo occurrence (left) and peak electron density (right) for 2010.  Four months are selected (one for each season) to show seasonal variations. In Figures \ref{fig:month_avg_occ}a--\ref{fig:month_avg_occ}d,  the pink line shows the 25\% occurrence contour that is used to define the echo band region. Black dots are the midpoints between the upper and lower portion of this contour.  A cosine function (white line) is fit to these points and used to model the echo band. The dashed white lines are the upper and lower bounds of the model band. The top right corner of each panel shows the parameters that characterize the band for that month: \(A\) is amplitude of cosine function (in km), \(B\) is time shift (in hrs), \(C\) is range shift from 0 (in km), and BW is the band width (constant distance between the upper and lower dashed white lines).  In Figures \ref{fig:month_avg_occ}e--\ref{fig:month_avg_occ}h the same echo location model is also given (white lines) along with expected echo locations based on raytracing simulations (dark red line).}
\label{fig:month_avg_occ}
\end{figure}

@@

\begin{figure}
\includegraphics[width=11.0 cm,angle=90]{year_month_analysis_line.pdf}
\caption{The variations in the echo band (a) amplitude of the fitted cosine function \(A\), (b) time shift or time of day of the peak \(B\), (c) average position of the band or the vertical shift of the cosine function from zero \(C\), and (d) width (BW). Different lines are for different years with the legend given in Figure \ref{fig:year_line}a.}
\label{fig:year_line}
\end{figure}

@@

\begin{figure}
\includegraphics[width=12.0 cm,angle=90]{year_month_analysis_color.pdf}
\caption{Contour plots of the (a)--(d) echo band range and (e)--(h) occurrence versus UT and season. Each row shows the data for a different year as given in the top-right corner.}
\label{fig:year_color}
\end{figure}

@@

\begin{figure}
\includegraphics[width=17.0 cm]{scatter_E2010.pdf}
\caption{The echo band range versus the (a) solar zenith angle (SZA) and (b) model peak F2 electron density (NmF2). Each point is color-coded in model \(E\) region density. Figures \ref{fig:scatter}c and d show the same but for the  echo occurrence within the band.}
\label{fig:scatter}
\end{figure}

@@

\begin{figure}
\includegraphics[width=15.0 cm]{IMF_vs_occ_MLT_avg.pdf}
\caption{IMF effects in echo occurrence. The echo occurrence versus UT was binned in 1-hr bins in UT and 2\% bins in occurrence and the average IMF (a) Bx, (b) By, and (c) Bz components over each plot cell are shown by the color.}
\label{fig:ut_occ}
\end{figure}

@@

\begin{figure}
\includegraphics[width=11.0 cm,angle=90]{occ_vs_IMF_avg.pdf}
\caption{Relative occurrence versus IMF By and Bz components for 6 different UT sectors. Each plot cell is color-coded based on the average relative occurrence over that cell.}
\label{fig:by_bz}
\end{figure}

@@

\begin{figure}
\includegraphics[width=18.0 cm]{Fig_RISR.pdf}
\caption{Conjugate measurements for two selected events on (left) March 14, 2010 and (right) April 6, 2010. Shown are the (a) and (e) IMF By (blue) and Bz (red) components, (b) and (f) MCM line-of-sight velocity versus UT and slant range in beam 14, (c) and (g) RKN velocity in beam 4, and (d) and (h) RISR-N electron density versus UT and altitude. The color bar is the same for the two middle rows and is given to the right of Figure \ref{fig:patchy_example}f.}
\label{fig:patchy_example}
\end{figure}

@@

\begin{figure}
\includegraphics[width=12.0 cm,angle=90]{month_ut_combined2010.pdf}
\caption{Contour plots of the (a) average occurrence within the band, (b) band range, (c) model peak F-region electron density (NmF2) and (d) solar zenith angle (SZA) versus UT and month in 2010. Color bars are given to the right. The white rectangle at the bottom of each panel is due to no data available in January 2010.}
\label{fig:month_ut}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=12.5 cm,angle=90]{p1f1.pdf}
\caption{Monthly average plots of echo occurrence (left) and peak electron density (right) for 2010.  Four months are selected (one for each season) to show seasonal variations. In Figures \ref{fig:month_avg_occ}a--\ref{fig:month_avg_occ}d,  the pink line shows the 25\% occurrence contour that is used to define the echo band region. Black dots are the midpoints between the upper and lower portion of this contour.  A cosine function (white line) is fit to these points and used to model the echo band. The dashed white lines are the upper and lower bounds of the model band. The top right corner of each panel shows the parameters that characterize the band for that month: \(A\) is amplitude of cosine function (in km), \(B\) is time shift (in hrs), \(C\) is range shift from 0 (in km), and BW is the band width (constant distance between the upper and lower dashed white lines).  In Figures \ref{fig:month_avg_occ}e--\ref{fig:month_avg_occ}h the same echo location model is also given (white lines) along with expected echo locations based on raytracing simulations (dark red line).}
\label{fig:month_avg_occ}
\end{figure}

@@

\begin{figure}
\includegraphics[width=11.0 cm,angle=90]{p1f2.pdf}
\caption{The variations in the echo band (a) amplitude of the fitted cosine function \(A\), (b) time shift or time of day of the peak \(B\), (c) average position of the band or the vertical shift of the cosine function from zero \(C\), and (d) width (BW). Different lines are for different years with the legend given in Figure \ref{fig:year_line}a.}
\label{fig:year_line}
\end{figure}

@@

\begin{figure}
\includegraphics[width=12.0 cm,angle=90]{p1f3.pdf}
\caption{Contour plots of the (a)--(d) echo band range and (e)--(h) occurrence versus UT and season. Each row shows the data for a different year as given in the top-right corner.}
\label{fig:year_color}
\end{figure}

@@

\begin{figure}
\includegraphics[width=17.0 cm]{p1f4.pdf}
\caption{The echo band range versus the (a) solar zenith angle (SZA) and (b) model peak F2 electron density (NmF2). Each point is color-coded in model \(E\) region density. Figures \ref{fig:scatter}c and d show the same but for the  echo occurrence within the band.}
\label{fig:scatter}
\end{figure}

@@

\begin{figure}
\includegraphics[width=15.0 cm]{p1f5.pdf}
\caption{IMF effects in echo occurrence. The echo occurrence versus UT was binned in 1-hr bins in UT and 2\% bins in occurrence and the average IMF (a) Bx, (b) By, and (c) Bz components over each plot cell are shown by the color.}
\label{fig:ut_occ}
\end{figure}

@@

%\begin{figure}
%\includegraphics[width=11.0 cm,angle=90]{occ_vs_IMF_avg.pdf}
%\caption{Relative occurrence versus IMF By and Bz components for 6 different UT sectors. Each plot cell is color-coded based on the average relative occurrence over that cell.}
%\label{fig:by_bz}
%\end{figure}

@@

\begin{figure}
\includegraphics[width=18.0 cm]{p1f6.pdf}
\caption{Conjugate measurements for two selected events on (left) March 14, 2010 and (right) April 6, 2010. Shown are the (a) and (e) IMF By (blue) and Bz (red) components, (b) and (f) MCM line-of-sight velocity versus UT and slant range in beam 14, (c) and (g) RKN velocity in beam 4, and (d) and (h) RISR-N electron density versus UT and altitude. The color bar is the same for the two middle rows and is given to the right of Figure \ref{fig:patchy_example}f.}
\label{fig:patchy_example}
\end{figure}

@@

\begin{figure}
\includegraphics[width=12.0 cm,angle=90]{p1f7.pdf}
\caption{Contour plots of the (a) average occurrence within the band, (b) band range, (c) model peak F-region electron density (NmF2) and (d) solar zenith angle (SZA) versus UT and month in 2010. Color bars are given to the right. The white rectangle at the bottom of each panel is due to no data available in January 2010.}
\label{fig:month_ut}
\end{figure}
